FictionEro - Data Cleaning

### 2024-05-24 analysis/1_cleaning.qmd
update data

df <- read.csv("../data/rawdata_participants.csv") |> 
  mutate(across(everything(), ~ifelse(.x == "", NA, .x))) |>
  mutate(Experimenter = case_when(
    Language=="English" & Experimenter %in% c("reddit7", "reddit8", "reddit1", "reddit2", "reddit5") ~ "Reddit (other)",
    .default = Experimenter
  ))

@@

plot_recruitement <- function(df) {
  # Consecutive count of participants per day (as area)
  df |>
    mutate(Date = as.Date(Date, format = "%d/%m/%Y")) |> 
    group_by(Date, Language, Experimenter) |> 
    summarize(N = n()) |> 
    ungroup() |>
    # https://bocoup.com/blog/padding-time-series-with-r
    complete(Date, Language, Experimenter, fill = list(N = 0)) |> 
    group_by(Language, Experimenter) |>
    mutate(N = cumsum(N)) |>
    ggplot(aes(x = Date, y = N)) +
    geom_area(aes(fill=Experimenter)) +
    scale_y_continuous(expand = c(0, 0)) +
    labs(
      title = "Recruitment History",
      x = "Date",
      y = "Total Number of Participants"
    ) +
    see::theme_modern() 
}

@@

# Table
table_recruitment <- function(df) {
  summarize(df, N = n(), .by=c("Language", "Experimenter")) |> 
    arrange(desc(N)) |> 
    gt::gt() |> 
    gt::opt_stylize() |> 
    gt::opt_interactive(use_compact_mode = TRUE) |> 
    gt::tab_header("Number of participants per recruitment source")
}
table_recruitment(df)
```

@@

```{r}
df |> 
  select(starts_with("Feedback"), -Feedback_Comments) |>
  pivot_longer(everything(), names_to = "Question", values_to = "Answer") |>
  group_by(Question, Answer) |> 
  summarise(prop = n()/nrow(df), .groups = 'drop') |> 
  complete(Question, Answer, fill = list(prop = 0)) |> 
  filter(Answer == "True") |> 
  mutate(Question = str_remove(Question, "Feedback_"),
         Question = str_replace(Question, "AILessArousing", "AI = Less arousing"),
         Question = str_replace(Question, "AIMoreArousing", "AI = More arousing"),
         Question = str_replace(Question, "CouldNotDiscriminate", "Hard to discriminate"),
         Question = str_replace(Question, "LabelsIncorrect", "Labels were incorrect"),
         Question = str_replace(Question, "NoFeels", "Didn't feel anything"),
         Question = str_replace(Question, "CouldDiscriminate", "Easy to discriminate"),
         Question = str_replace(Question, "LabelsReversed", "Labels were reversed")) |>
  mutate(Question = fct_reorder(Question, desc(prop))) |> 
  ggplot(aes(x = Question, y = prop)) +
  geom_bar(stat = "identity") +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks(), labels=scales::percent) +
  labs(x="Feedback", y = "Participants", title = "Feedback") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1), angle = 45, hjust = 1),
    axis.title.x = element_blank()
  )
```

@@

```{r}
data.frame(Language = df$Language,
           Source = df$Experimenter,
           Comments = trimws(df$Feedback_Comments)) |> 
  filter(!tolower(Comments) %in% c(NA, "no", "nope", "none", "na", "n/a", "non")) |> 
  arrange(Language, Source) |>
  gt::gt() |> 
  gt::opt_stylize() |> 
  gt::opt_interactive(use_compact_mode = TRUE) 
```

@@

outliers <- c(
  # "S206"  # Collapsed RTs in both phases
  # "S399"  # Negative Arousal-Valence correlations
)
potentials <- list()
```

@@

We removed `r sum(df$Mobile=="True")` participants that participated with a mobile device.

```{r}
df <- filter(df, Mobile == "False")
dftask <- filter(dftask, Participant %in% df$Participant)
```

@@

df |>
  mutate(Participant = fct_reorder(Participant, Experiment_Duration),
         Category = ifelse(Experiment_Duration > 60, "extra", "ok"),
         Duration = ifelse(Experiment_Duration > 60, 60, Experiment_Duration),
         Group = ifelse(Participant %in% outliers, "Outlier", "ok")) |>
  ggplot(aes(y = Participant, x = Duration)) +
  geom_point(aes(color = Group, shape = Category)) +
  geom_vline(xintercept = median(df$Experiment_Duration), color = "red", linetype = "dashed") +
  scale_shape_manual(values = c("extra" = 3, ok = 19)) +
  scale_color_manual(values = c("Outlier" = "red", ok = "black"), guide="none") +
  guides(color = "none", shape = "none") +
  ggside::geom_xsidedensity(fill = "#4CAF50", color=NA) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  labs(
    title = "Experiment Completion Time",
    x = "Duration (in minutes)",
    y = "Participant"
  )  +
  theme_bw() +
  ggside::theme_ggside_void() +
  theme(ggside.panel.scale = .3,
        panel.border = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

potentials$expe_duration <- arrange(df, Experiment_Duration) |>
  select(Participant, Experiment_Duration) |>
  head(5) 
```

@@

df |>
  mutate(Participant = fct_reorder(Participant, BAIT_Duration),
         Category = ifelse(BAIT_Duration > 5, "extra", "ok"),
         Duration = ifelse(BAIT_Duration > 5, 5, BAIT_Duration),
         Group = ifelse(Participant %in% outliers, "Outlier", "ok")) |>
  ggplot(aes(y = Participant, x = Duration)) +
  geom_point(aes(color = Group, shape = Category)) +
  geom_vline(xintercept = median(df$BAIT_Duration), color = "red", linetype = "dashed") +
  scale_shape_manual(values = c("extra" = 3, ok = 19)) +
  scale_color_manual(values = c("Outlier" = "red", ok = "black"), guide="none") +
  guides(color = "none", shape = "none") +
  ggside::geom_xsidedensity(fill = "#9C27B0", color=NA) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  labs(
    title = "Questionnaire Completion Time",
    x = "Duration (in minutes)",
    y = "Participant"
  )  +
  theme_bw() +
  ggside::theme_ggside_void() +
  theme(ggside.panel.scale = .3,
        panel.border = element_blank(),
        axis.ticks.y = element_blank(),
          axis.text.y = element_blank()) 
```

@@

@@

potentials$emo_diff <- arrange(dat, Arousal) |>
  head(5)
```

@@

```{r}
# Single arousal response (0)
outliers <- summarize(dftask, n = length(unique(Arousal)), .by="Participant") |> 
  filter(n == 1) |> 
  select(Participant) |> 
  pull() |> 
  c(outliers)

dat <- dftask |> 
  filter(!Participant %in% outliers) |> 
  summarize(cor_ArVal = cor(Arousal, Valence),
            cor_ArEnt = cor(Arousal, Enticement),
            .by="Participant")

@@

potentials$emo_cor <- arrange(dat, cor_ArVal) |>
  head(5)
```

We removed `r length(outliers)` that showed no variation in their arousal response.

```{r}
# c(as.character(potentials$expe_duration$Participant), 
#   as.character(potentials$emo_diff$Participant), 
#   as.character(potentials$emo_cor$Participant)) |> 
#   table()
#   
df <- filter(df, !Participant %in% outliers)
dftask <- filter(dftask, !Participant %in% outliers)
```

@@

```{r}
df <- filter(df, !Participant %in% outliers)
dftask <- filter(dftask, !Participant %in% outliers)
```

@@

df |> 
  ggplot(aes(x = Screen_Size)) +
  geom_histogram() +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  labs(x =  expression("Screen Size ("~sqrt(Number~of~Pixels)~")"), y = "Number of Participants", title = "Screen Size") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1))
  )
```

@@

```{r}
bait <- df |> 
  select(starts_with("BAIT_"), -BAIT_Duration) |> 
  rename_with(function(x) gsub("BAIT_\\d_", "", x))

@@

efa <- parameters::factor_analysis(bait, cor=cor(bait), n=3, rotation = "oblimin", 
                                   sort=TRUE, scores="tenBerge", fm="ml")
plot(efa)
display(efa)
```

@@

# bayestestR::bayesfactor_models(m1, m2)
lavaan::anova(m1, m2, m3, m4, m5)
```
```{r}
display(parameters::parameters(m3, standardize = TRUE))
```

@@

```{r}
ega_final <- ega$glasso_walktrap_riEGA$EGA
plot(ega_final)

ega_scores <-  EGAnet::net.scores(bait, ega_final)$scores$std.scores |> 
  as.data.frame() |> 
  setNames(c("EGA_Image", "EGA_Videos", "EGA_Text")) 
```

@@

# Merge with data
scores <- lavaan::predict(m3) |> 
  as.data.frame() |> 
  datawizard::data_addprefix("CFA_") |> 
  # data_rename(c("ML1", "ML2"), c("BAIT_SEM1", "BAIT_SEM2")) |> 
  cbind(ega_scores) |> 
  mutate(Participant = df$Participant)

scores$BAIT_Videos <- (bait$VideosRealistic + (1 - bait$VideosIssues)) / 2
scores$BAIT_Images <- (bait$ImagesRealistic + (1 - bait$ImagesIssues) + bait$ImitatingReality + bait$EnvironmentReal) / 4
scores$BAIT_Text <- (bait$TextRealistic + (1 - bait$TextIssues)) / 2

df <- merge(df, scores, by="Participant")
```

@@

```{r}
correlation::cor_test(scores, "BAIT_Images", "CFA_Images") |> 
  plot() +
  ggside::geom_xsidedensity(aes(x=BAIT_Images), color="grey", linewidth=1) +
  ggside::geom_ysidedensity(aes(y=CFA_Images), color="grey", linewidth=1) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
  ggside::theme_ggside_void() +
  theme(ggside.panel.scale = .1) 
```

@@

```{r}
table <- correlation::correlation(
  select(scores, starts_with("BAIT_")), 
  select(df, starts_with("GAAIS")),
  bayesian=TRUE) |> 
  summary()

@@

```{r}
df |> 
  ggplot(aes(x=as.factor(AI_Knowledge), y=BAIT_Images)) +
  geom_boxplot()

# m <- betareg::betareg(BAIT ~ AI_Knowledge, data=df)
m <- lm(BAIT_Images ~ poly(AI_Knowledge, 2), data=df)
# m <- brms::brm(BAIT ~ mo(AI_Knowledge), data=df, algorithm = "meanfield")
# m <- brms::brm(BAIT ~ AI_Knowledge, data=dfsub, algorithm = "meanfield")
display(parameters::parameters(m))

marginaleffects::predictions(m, by=c("AI_Knowledge"), newdata = "marginalmeans") |> 
  as.data.frame() |> 
  ggplot(aes(x=AI_Knowledge, y=estimate)) +
  geom_jitter2(data=df, aes(y=BAIT_Images), alpha=0.2, width=0.1) +
  geom_line(aes(group=1), position = position_dodge(width=0.2)) +
  geom_pointrange(aes(ymin = conf.low, ymax=conf.high), position = position_dodge(width=0.2)) +
  theme_minimal() +
  labs(x = "AI-Knowledge", y="BAIT Score")
```

@@

```{r}
# m <- betareg::betareg(BAIT ~ Sex / Age, data=df, na.action=na.omit)
m <- lm(BAIT_Images ~ Sex / Age, data=df)
display(parameters::parameters(m))
```

@@

```{r}
glm(Feedback_LabelsIncorrect ~ BAIT_Images * AI_Knowledge, 
    data=mutate(df, Feedback_LabelsIncorrect = ifelse(Feedback_LabelsIncorrect=="True", 1, 0)), 
    family="binomial") |> 
  parameters::parameters() |> 
  display(title="Predicting 'Labels are Incorrect'")
```

```{r}
glm(Feedback_LabelsReversed ~ BAIT_Images * AI_Knowledge, 
    data=mutate(df, Feedback_LabelsReversed = ifelse(Feedback_LabelsReversed=="True", 1, 0)), 
    family="binomial") |> 
  parameters::parameters() |> 
  display(title="Predicting 'Labels are reversed'")
```

```{r}
glm(Feedback_CouldDiscriminate ~ BAIT_Images * AI_Knowledge, 
    data=mutate(df, Feedback_CouldDiscriminate = ifelse(Feedback_CouldDiscriminate=="True", 1, 0)), 
    family="binomial") |> 
  parameters::parameters() |> 
  display(title="Predicting 'Easy to discriminate'")
```

```{r}
glm(Feedback_CouldNotDiscriminate ~ BAIT_Images * AI_Knowledge, 
    data=mutate(df, Feedback_CouldNotDiscriminate = ifelse(Feedback_CouldNotDiscriminate=="True", 1, 0)), 
    family="binomial") |> 
  parameters::parameters() |> 
  display(title="Predicting 'Hard to discriminate'")
```

```{r}
glm(Feedback_Fun ~ BAIT_Images * AI_Knowledge, 
    data=mutate(df, Feedback_Fun = ifelse(Feedback_Fun=="True", 1, 0)), 
    family="binomial") |> 
  parameters::parameters() |> 
  display(title="Predicting 'Fun'")
```

```{r}
glm(Feedback_Boring ~ BAIT_Images * AI_Knowledge, 
    data=mutate(df, Feedback_Boring = ifelse(Feedback_Boring=="True", 1, 0)), 
    family="binomial") |> 
  parameters::parameters() |> 
  display(title="Predicting 'Boring'")
```

>>>>

df <- read.csv("../data/rawdata_participants.csv") |> 
  mutate(across(everything(), ~ifelse(.x == "", NA, .x))) |>
  mutate(Sample = case_when(
    Language=="English" & str_detect(Experimenter, "reddit") ~ "Reddit",
    Language=="English" & Experimenter %in% c("2discord1", "Experimenter2", "Experimenter1") ~ "Student",
    Language=="English" & Experimenter %in% c("Unknown", "Readme (GitHub)", "website") ~ "Other",
    .default = Experimenter
  ))

@@

```{r}
#| message: false
#| fig-width: 12
#| fig-height: 12

plot_recruitement <- function(df) {
  # Consecutive count of participants per day (as area)
  df |>
    mutate(Date = as.Date(Date, format = "%d/%m/%Y")) |> 
    group_by(Date, Language, Sample) |> 
    summarize(N = n()) |> 
    ungroup() |>
    # https://bocoup.com/blog/padding-time-series-with-r
    complete(Date, Language, Sample, fill = list(N = 0)) |> 
    group_by(Language, Sample) |>
    mutate(N = cumsum(N)) |>
    ggplot(aes(x = Date, y = N)) +
    geom_area(aes(fill=Sample)) +
    scale_y_continuous(expand = c(0, 0)) +
    labs(
      title = "Recruitment History",
      x = "Date",
      y = "Total Number of Participants"
    ) +
    see::theme_modern() 
}

@@

# Table
table_recruitment <- function(df) {
  summarize(df, N = n(), .by=c("Language", "Sample")) |> 
    arrange(desc(N)) |> 
    gt::gt() |> 
    gt::opt_stylize() |> 
    gt::opt_interactive(use_compact_mode = TRUE) |> 
    gt::tab_header("Number of participants per recruitment source")
}
table_recruitment(df)
```

@@

```{r}
df |> 
  select(starts_with("Feedback"), -Feedback_Comments) |>
  pivot_longer(everything(), names_to = "Question", values_to = "Answer") |>
  group_by(Question, Answer) |> 
  summarise(prop = n()/nrow(df), .groups = 'drop') |> 
  complete(Question, Answer, fill = list(prop = 0)) |> 
  filter(Answer == "True") |> 
  mutate(Question = str_remove(Question, "Feedback_"),
         Question = str_replace(Question, "AILessArousing", "AI = Less arousing"),
         Question = str_replace(Question, "AIMoreArousing", "AI = More arousing"),
         Question = str_replace(Question, "CouldNotDiscriminate", "Hard to discriminate"),
         Question = str_replace(Question, "LabelsIncorrect", "Labels were incorrect"),
         Question = str_replace(Question, "NoFeels", "Didn't feel anything"),
         Question = str_replace(Question, "CouldDiscriminate", "Easy to discriminate"),
         Question = str_replace(Question, "LabelsReversed", "Labels were reversed")) |>
  mutate(Question = fct_reorder(Question, desc(prop))) |> 
  ggplot(aes(x = Question, y = prop)) +
  geom_bar(stat = "identity") +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks(), labels=scales::percent) +
  labs(x="Feedback", y = "Participants", title = "Feedback") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1), angle = 45, hjust = 1),
    axis.title.x = element_blank()
  )
```

@@

```{r}
data.frame(Language = df$Language,
           Source = df$Experimenter,
           Comments = trimws(df$Feedback_Comments)) |> 
  filter(!tolower(Comments) %in% c(NA, "no", "nope", "none", "na", "n/a", "non", ".", "..", "ninguno")) |> 
  arrange(Language, Source) |>
  gt::gt() |> 
  gt::opt_stylize() |> 
  gt::opt_interactive(use_compact_mode = TRUE) 
```

@@

outliers <- list()
```

@@

There were `r sum(df$Mobile=="True")` participants that used a mobile device.

```{r}
# df <- filter(df, Mobile == "False")
dftask <- filter(dftask, Participant %in% df$Participant)
```

@@

df |>
  mutate(Participant = fct_reorder(Participant, Experiment_Duration),
         Category = ifelse(Experiment_Duration > 60, "extra", "ok"),
         Duration = ifelse(Experiment_Duration > 60, 60, Experiment_Duration),
         Group = ifelse(Participant %in% outliers, "Outlier", "ok")) |>
  ggplot(aes(y = Participant, x = Duration)) +
  geom_point(aes(color = Group, shape = Category)) +
  geom_vline(xintercept = median(df$Experiment_Duration), color = "red", linetype = "dashed") +
  geom_vline(xintercept = 15, color = "orange", linetype = "dotted") +
  scale_shape_manual(values = c("extra" = 3, ok = 19)) +
  scale_color_manual(values = c("Outlier" = "red", ok = "black"), guide="none") +
  guides(color = "none", shape = "none") +
  ggside::geom_xsidedensity(fill = "#4CAF50", color=NA) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  labs(
    title = "Experiment Completion Time",
    x = "Duration (in minutes)",
    y = "Participants"
  )  +
  theme_modern() +
  ggside::theme_ggside_void() +
  theme(ggside.panel.scale = .3,
        panel.border = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

outliers$expe_duration <- filter(df, Experiment_Duration < 15)$Participant
```

@@

df |>
  mutate(Participant = fct_reorder(Participant, BAIT_Duration),
         Category = ifelse(BAIT_Duration > 5, "extra", "ok"),
         Duration = ifelse(BAIT_Duration > 5, 5, BAIT_Duration),
         Group = ifelse(Participant %in% outliers, "Outlier", "ok")) |>
  ggplot(aes(y = Participant, x = Duration)) +
  geom_point(aes(color = Group, shape = Category)) +
  geom_vline(xintercept = median(df$BAIT_Duration), color = "red", linetype = "dashed") +
  geom_vline(xintercept = 0.5, color = "orange", linetype = "dotted") +
  scale_shape_manual(values = c("extra" = 3, ok = 19)) +
  scale_color_manual(values = c("Outlier" = "red", ok = "black"), guide="none") +
  guides(color = "none", shape = "none") +
  ggside::geom_xsidedensity(fill = "#9C27B0", color=NA) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  labs(
    title = "Questionnaire Completion Time",
    x = "Duration (in minutes)",
    y = "Participant"
  )  +
  theme_modern() +
  ggside::theme_ggside_void() +
  theme(ggside.panel.scale = .3,
        panel.border = element_blank(),
        axis.ticks.y = element_blank(),
          axis.text.y = element_blank())

outliers$bait_duration <- filter(df, BAIT_Duration < 0.5)$Participant
df[df$Participant %in% outliers$bait_duration, str_detect(names(df), "BAIT_\\d+")] <- NA
```

We excluded the BAIT data of `r length(outliers$bait_duration)` participants who completed the questionnaire in less than 30 seconds.

@@

```{r}
# Single arousal response (0)
outliers$novariability <- summarize(dftask, n = length(unique(Arousal)), .by="Participant") |> 
  filter(n == 1) |> 
  select(Participant) |> 
  pull()

df <- filter(df, !Participant %in% outliers$novariability)
dftask <- filter(dftask, !Participant %in% outliers$novariability)
```

We removed `r length(outliers$novariability)` that showed no variation in their arousal response (did not move the scales).

@@

outliers$emo_diff <- sort(as.character(dat[dat$Arousal < 0, ]$Participant))
```

@@

```{r}
dat <- dftask |> 
  filter(!Participant %in% outliers) |> 
  summarize(cor_ArVal = cor(Arousal, Valence),
            cor_ArEnt = cor(Arousal, Enticement),
            .by="Participant")

@@

outliers$emo_cor <- sort(as.character(dat[dat$cor_ArEnt < 0, ]$Participant))

outliers$arousal <- intersect(outliers$emo_diff, outliers$emo_cor)
```

We removed `r length(outliers$arousal)` participants that had a negative correlation between arousal and enticement, and had a negative arousal difference between erotic and neutral (suggesting a misunderstanding of the scale direction).

```{r}
df <- filter(df, !Participant %in% outliers$arousal)
dftask <- filter(dftask, !Participant %in% outliers$arousal)
```

@@

@@

df |> 
  ggplot(aes(x = Screen_Size, fill=Mobile)) +
  geom_histogram(bins = 50, color="black") +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  labs(x =  expression("Screen Size ("~sqrt(Number~of~Pixels)~")"), y = "Number of Participants", title = "Screen Size") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1))
  )
```

@@

```{r}
bait <- df |> 
  select(starts_with("BAIT_"), -BAIT_Duration) |> 
  rename_with(function(x) gsub("BAIT_\\d_", "", x)) |> 
  filter(!is.na(TextRealistic ))

@@

efa <- parameters::factor_analysis(bait, cor=cor(bait, use="pairwise.complete.obs"), n=3, rotation = "oblimin", 
                                   sort=TRUE, scores="tenBerge", fm="ml")
plot(efa)
display(efa)
```

@@

# bayestestR::bayesfactor_models(m1, m2)
lavaan::anova(m1, m2, m3, m4, m5)
```
```{r}
display(parameters::parameters(m4, standardize = TRUE))
```

```{r}
m4b <- lavaan::sem(
  "Environment =~ ImitatingReality + EnvironmentReal 
  Images =~ ImagesRealistic + ImagesIssues
  Videos =~ VideosIssues + VideosRealistic
  Text =~ TextIssues + TextRealistic
  G =~ Environment + Images + Videos + Text", 
  data=bait)

m4c <- lavaan::sem(
  "Environment =~ ImitatingReality + EnvironmentReal 
  Images =~ ImagesRealistic + ImagesIssues
  Videos =~ VideosIssues + VideosRealistic
  Text =~ TextIssues + TextRealistic
  Visual =~ Environment + Images", 
  data=bait)

# bayestestR::bayesfactor_models(m1, m2)
lavaan::anova(m4, m4b, m4c)
```

```{r}
display(parameters::parameters(m4c, standardize = TRUE))
```

library(ggraph)
library(tidySEM)

edges <- tidySEM::get_edges(m4c) |> 
  mutate(sign = as.factor(sign(as.numeric(est_std))))

tidygraph::tbl_graph(nodes = tidySEM::get_nodes(m4c), edges = edges) |> 
  ggraph(layout = 'kk') + 
  geom_edge_link(aes(filter=op=="=~", label=est_std, color=sign),
                 angle_calc="along",
                 label_dodge=unit(-0.015, "npc"),
                 edge_width=1) + 
  geom_edge_arc(aes(filter=op=="~~", label=est_std, color=sign), 
                linetype="dashed", strength=0.1,
                angle_calc="along",
                label_dodge=unit(-0.015, "npc"),
                edge_width=1) + 
  geom_node_point(aes(shape=shape, color=shape), size=14, alpha=0.3) +
  geom_node_text(aes(label = name)) + 
  scale_edge_color_manual(values=c("1"="darkgreen", "-1"="red"), guide="none") +
  scale_shape_manual(values=c("oval"="circle", "rect"="square"), guide="none") +
  scale_color_manual(values=c("oval"="orange", "rect"="black"), guide="none") +
  theme_void()
```

@@

```{r}
ega_final <- ega$glasso_walktrap_riEGA$EGA
plot(ega_final)
```

@@

# Merge with data
ega_scores <-  EGAnet::net.scores(bait, ega_final)$scores$std.scores |> 
  as.data.frame() |> 
  setNames(c("BAIT_Text_EGA", "BAIT_Visual_EGA", "BAIT_Videos_EGA"))

sem_scores <- lavaan::predict(m4c) |> 
  as.data.frame() |> 
  datawizard::data_addprefix("BAIT_") |> 
  datawizard::data_addsuffix("_SEM")

raw_scores <- data.frame(
  Participant = df[!is.na(df$BAIT_1_ImagesRealistic), ]$Participant,
  BAIT_Videos = (bait$VideosRealistic + (1 - bait$VideosIssues)) / 2,
  BAIT_Visual = (bait$ImagesRealistic + (1 - bait$ImagesIssues) + bait$ImitatingReality + bait$EnvironmentReal) / 4,
  BAIT_Text = (bait$TextRealistic + (1 - bait$TextIssues)) / 2
  )

scores <- cbind(sem_scores, ega_scores, raw_scores) 
df <- merge(df, raw_scores, by="Participant")
```

@@

```{r}
correlation::cor_test(scores, "BAIT_Visual", "BAIT_Visual_SEM") |> 
  plot() +
  ggside::geom_xsidedensity(aes(x=BAIT_Visual), color="grey", linewidth=1) +
  ggside::geom_ysidedensity(aes(y=BAIT_Visual_SEM), color="grey", linewidth=1) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
  ggside::theme_ggside_void() +
  theme(ggside.panel.scale = .1) 
```

@@

```{r}
table <- correlation::correlation(
  select(df, all_of(names(raw_scores))), 
  select(df, starts_with("GAAIS")),
  bayesian=TRUE) |> 
  summary()

@@

```{r}
df |> 
  ggplot(aes(x=as.factor(AI_Knowledge), y=BAIT_Visual)) +
  geom_boxplot()

# m <- betareg::betareg(BAIT ~ AI_Knowledge, data=df)
m <- lm(BAIT_Visual ~ poly(AI_Knowledge, 2), data=df)
# m <- brms::brm(BAIT ~ mo(AI_Knowledge), data=df, algorithm = "meanfield")
# m <- brms::brm(BAIT ~ AI_Knowledge, data=dfsub, algorithm = "meanfield")
display(parameters::parameters(m))

marginaleffects::predictions(m, by=c("AI_Knowledge"), newdata = "marginalmeans") |> 
  as.data.frame() |> 
  ggplot(aes(x=AI_Knowledge, y=estimate)) +
  ggdist::stat_halfeye(data=df, aes(y=BAIT_Visual), geom="slab") +
  # ggdist::stat_dots(data=df, aes(y=BAIT_Visual), side="left") +
  # geom_boxplot(data=df, aes(y=BAIT_Visual, group=AI_Knowledge)) +
  geom_point2(data=df, aes(x=AI_Knowledge-0.08, y=BAIT_Visual), alpha=0.2, position=position_jitter(width=0.06), size=2) +
  geom_line(aes(group=1), position = position_dodge(width=0.2)) +
  geom_pointrange(aes(ymin = conf.low, ymax=conf.high), position = position_dodge(width=0.2)) +
  theme_minimal() +
  labs(x = "AI-Knowledge", y="BAIT - Visual")
```

@@

```{r}
# m <- betareg::betareg(BAIT ~ Sex / Age, data=df, na.action=na.omit)
m <- lm(BAIT_Visual ~ Sex / Age, data=df)
display(parameters::parameters(m))
```

@@

```{r}
glm(Feedback_LabelsIncorrect ~ BAIT_Visual * AI_Knowledge, 
    data=mutate(df, Feedback_LabelsIncorrect = ifelse(Feedback_LabelsIncorrect=="True", 1, 0)), 
    family="binomial") |> 
  parameters::parameters() |> 
  display(title="Predicting 'Labels are Incorrect'")
```

```{r}
glm(Feedback_LabelsReversed ~ BAIT_Visual * AI_Knowledge, 
    data=mutate(df, Feedback_LabelsReversed = ifelse(Feedback_LabelsReversed=="True", 1, 0)), 
    family="binomial") |> 
  parameters::parameters() |> 
  display(title="Predicting 'Labels are reversed'")
```

```{r}
glm(Feedback_CouldDiscriminate ~ BAIT_Visual * AI_Knowledge, 
    data=mutate(df, Feedback_CouldDiscriminate = ifelse(Feedback_CouldDiscriminate=="True", 1, 0)), 
    family="binomial") |> 
  parameters::parameters() |> 
  display(title="Predicting 'Easy to discriminate'")
```

```{r}
m <- glm(Feedback_CouldNotDiscriminate ~ BAIT_Visual * AI_Knowledge, 
    data=mutate(df, Feedback_CouldNotDiscriminate = ifelse(Feedback_CouldNotDiscriminate=="True", 1, 0)), 
    family="binomial")

parameters::parameters(m) |> 
  display(title="Predicting 'Hard to discriminate'")

modelbased::estimate_relation(m, length=6) |> 
  plot()
```

```{r}
glm(Feedback_Fun ~ BAIT_Visual * AI_Knowledge, 
    data=mutate(df, Feedback_Fun = ifelse(Feedback_Fun=="True", 1, 0)), 
    family="binomial") |> 
  parameters::parameters() |> 
  display(title="Predicting 'Fun'")
```

```{r}
glm(Feedback_Boring ~ BAIT_Visual * AI_Knowledge, 
    data=mutate(df, Feedback_Boring = ifelse(Feedback_Boring=="True", 1, 0)), 
    family="binomial") |> 
  parameters::parameters() |> 
  display(title="Predicting 'Boring'")
```
